%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\begin{cventries}

\cventry
    {Engineering} % Job title
    {ONE} % Organization
    {Hyderabad, India} % Location
    {Jan. 2024 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Leading a team responsible for maintaining the core banking and risk engineering platform for the firm.}
        \item {Primary goals include maintaining unified patterns to interacting with banking ledger related vendors and also a near no-code platform for risk policy teams to deploy risk detection and analysis pieces.}
        \item {Conceptualized and build a stateful replica of our banking ledger using AWS native components and CDC for data replication which works at scale servine more than 1.5MM customers.}
      \end{cvitems}
    }
%---------------------------------------------------------

\cventry
    {Senior Software Engineer} % Job title
    {Microsoft India Development Center} % Organization
    {Hyderabad, India} % Location
    {Aug. 2021 - Jan. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Worked with Azure Data organisation to build tools and services for helping with database modernisation (cloud migration and hybrid management.)}
        \item {Developed an extension for Azure Data Studio which helps in offline assessment of Oracle Databases.}
        \item {Worked on building a cloud based solution for customers to be able to modernize their database estate, by discovering, assessing and building business cases at-scale to determine migration/hybrid management path.}
        \item {Conceptualized and prototyped a migration of the above service from a legacy stack to the latest pattern of Azure Arc which uses k8s native services.}
      \end{cvitems}
    }
%---------------------------------------------------------

\cventry
    {Software Engineering Analyst} % Job title
    {Goldman Sachs} % Organization
    {Bangalore, India} % Location
    {Jul. 2019 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Worked in development of Apple Card platform for Marcus, a consumer bank by Goldman Sachs.}
        \item {Developed shared services and libraries to be used across cloud platform for solving common concerns like security, crypto, data etc.}
        \item {Maintained large scale Mongo deployments in association with MongoDB Atlas.}
        \item {Developed a change-data-capture platform to help with data governance and compliance.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Samsung R\&D Institute} % Organization
    {Bangalore, India} % Location
    {Jun. 2018 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Involved in Development Deep Neural Models for large class Object Recognition.}
        \item {The models are designed keeping in mind they are to be deployed on-device. These are trained using Caffe as a framework.}
        \item {Developed several modules in C++ of the core on-device AI engine behind Bixby Vision, which deploys the above models on Flagship devices.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Microsoft India Development Center} % Organization
    {Hyderabad, India} % Location
    {Jan. 2018 - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed various native C++ and Android modules of an SDK to help anyone make custom chat cards in Microsoft Kaizala.}
        \item {Chat Cards are HTML pages which can be used for purposes like taking a Poll or playing arcade games with leaderboard in a group.}
        \item {Involved in development and maintenance of some out-of-the box game chat cards like 2048.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Samsung R\&D Institute} % Organization
    {Bangalore, India} % Location
    {Jun. 2017 - Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a statistical model for ranking objects to improve user experience.}
        \item {Deployed the above model as a RESTful API for My Galaxy App used in most Samsung Mobile Devices.}
      \end{cvitems}
    }

%---------------------------------------------------------


  \cventry
    {Summer Intern (under Prof.G Nagarjuna)} % Job title
    {HBCSE, Tata Institute Fundamental Research} % Organization
    {Mumbai, India} % Location
    {May. 2016 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and interactive dashboard for Data Analytics of MetaStudio, a GNU project subsidiary.}
        \item {The feature involved developing a visualization dashboard to provide the admin a sublime analytics of data being collected from schools across 4 Indian states}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
